Twists of supersymmetric gauge theories

### 2019-05-06 paper.tex
merge
the definition of a classical theory

% field theories defined in terms of vector bundles on spacetime
% explain how to obtain a QP manifold
% explain how to obtain a factorization algebra given a classical solution

@@

>>>>

\subsection{The definition of a field theory}
% field theories defined in terms of vector bundles on spacetime

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ$-graded vector bundle $E \to M$ equipped with a differential operator of cohomological degree $+1$
\[
Q : \cE \to \cE [1] 
\]
such that (1) $Q^2 = 0$ and (2) $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega : E \otimes E \to {\rm Dens}_M [-1]
\]
that is (1) fiberwise nondegenerate, (2) graded skew symmetric, and (3) satisfies $\int_M \omega\<e_0, Qe_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{itemize}
\end{dfn}

\begin{dfn}
A {\bf classical field theory} is a free classical field theory $(E, Q, \omega)$ equipped with a functional
\[
I \in \oloc^+(E)
\]
satisfying the classical master equation 
\[
Q I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(E), Q + \{I,-\}\right) .
\]
We will refer to this as the classical BV complex of the theory.

\begin{dfn}
A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
\[
F : E \to E'
\]
that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
\end{dfn}

Note that a map of classical field theories induces a map of BV complexes
\[
F^* : \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

\begin{dfn}
A map of classical field theories $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
\[
F^* :  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{dfn}

% explain how to obtain a QP manifold

% explain how to obtain a factorization algebra given a classical solution

@@

\subsubsection{The minimal twist}
